\vspace{-1em}Guidance, please! Towards a framework for RDF-based constraint languages.

### 2015-07-16 paper/paper 2/dc-2015.tex
minor

Various constraint languages exist or are being developed that support more or less of these constraint types. For our work, we focus on the following four as the ones that are most popular among data practitioners, often mentioned on mailing lists and/or being candidates or prototypes for the upcoming W3C recommendation:
\emph{Description Set Profiles (DSP)}, \emph{Resource Shapes (ReSh)}, \emph{Shape Expressions (ShEx)}\footnote{\url{http://www.w3.org/Submission/2014/SUBM-shex-primer-20140602/}}, and the \emph{Web Ontology Language} \emph{(OWL)}. Despite the fact that OWL is arguably not a constraint language, it is widely used in practice as such under the closed-world and unique name assumptions.

@@

The \emph{DCMI Abstract Model} \cite{DCMI-Abstract-Model-2007} is required for formalizing a notion of machine-processable application profiles. It specifies an abstract model for Dublin Core metadata which is independent of any particular encoding syntax. Its primary purpose is to specify the components used in Dublin Core metadata. Nilsson et al. \cite{DCMI-DC-RDF-2008} depict how the constructs of the DCMI Abstract Model are represented using the abstract syntax of the RDF model. A \emph{Description Set Profile (DSP)} \cite{DCMI-DSP-2008} is a generic constraint language which is used to formally specify structural constraints on sets of resource descriptions within an application profile. DSP constrains resources that may be described by descriptions in a description set, the properties that may be used, and the values properties may point to. \emph{BIBFRAME}\footnote{\url{http://bibframe.org}} \cite{Kroeger-2013,Godby-2015,Miller-2012} is the result of the \emph{Bibliographic Framework Initiative} and defines a vocabulary \cite{DCMI-Bibframe-Authorities-2014,DCMI-Bibframe-Relationships-2014} which has a strong overlap with DSP. \emph{BIBFRAME Profiles} \cite{DCMI-Bibframe-Profiles-2014} are essentially identical to DCAPs.

>>>>

Various constraint languages exist or are being developed that support more or less of these constraint types. For our work, we focus on the following four as the ones that are most popular among data practitioners, often mentioned on mailing lists and/or being candidates or prototypes for the upcoming W3C recommendation:
\emph{Description Set Profiles (DSP)}\footnote{\url{ http://dublincore.org/documents/2008/03/31/dc-dsp/}}, \emph{Resource Shapes (ReSh)}, \emph{Shape Expressions (ShEx)}\footnote{\url{http://www.w3.org/Submission/2014/SUBM-shex-primer-20140602/}}, and the \emph{Web Ontology Language} \emph{(OWL)}. Despite the fact that OWL is arguably not a constraint language, it is widely used in practice as such under the closed-world and unique name assumptions.

@@

The \emph{DCMI Abstract Model} \cite{DCMI-Abstract-Model-2007} is required for formalizing a notion of machine-processable application profiles. It specifies an abstract model for Dublin Core metadata which is independent of any particular encoding syntax. Its primary purpose is to specify the components used in Dublin Core metadata. Nilsson et al. \cite{DCMI-DC-RDF-2008} depict how the constructs of the DCMI Abstract Model are represented using the abstract syntax of the RDF model. A \emph{Description Set Profile (DSP)}\footnote{\url{ http://dublincore.org/documents/2008/03/31/dc-dsp/}} \cite{DCMI-DSP-2008} is a generic constraint language which is used to formally specify structural constraints on sets of resource descriptions within an application profile. DSP constrains resources that may be described by descriptions in a description set, the properties that may be used, and the values properties may point to. \emph{BIBFRAME}\footnote{\url{http://bibframe.org}} \cite{Kroeger-2013,Godby-2015,Miller-2012} is the result of the \emph{Bibliographic Framework Initiative} and defines a vocabulary \cite{DCMI-Bibframe-Authorities-2014,DCMI-Bibframe-Relationships-2014} which has a strong overlap with DSP. \emph{BIBFRAME Profiles} \cite{DCMI-Bibframe-Profiles-2014} are essentially identical to DCAPs.
